A cautionary note on the use of Ornstein Uhlenbeck models in macroevolutionary studies

### 2015-05-11 Manuscript/ohyou_wordconvert.tex
Merged GHTs edits

\usepackage[osf]{mathpazo} % palatino
\usepackage{ms}            % load the template
\usepackage[round]{natbib} % author-year citations
\usepackage{graphicx}
\usepackage{parskip} 
\usepackage{enumerate} 
\usepackage{longtable}
\usepackage{pdflscape}
\usepackage{fullpage}
\usepackage{hyperref}
%\usepackage[nomarkers, nolists]{endfloat}  % To push floats to the end   
\pagenumbering{arabic}

@@

    \begin{figure}[!htbp]
      \centering
      \includegraphics[width=10cm, height=10cm, keepaspectratio=true]{Figures/OhYou_Figure1.pdf}
      \caption{The number of ecology, evolutionary biology and palaeontology papers published between 2005 and 2014 containing the phrase ``Ornstein-Uhlenbeck'', as a proportion of the total number of ecology, evolutionary biology or palaeontology papers published that year. See Supporting Information for details.
      }
      \label{figure.literature}
\end{figure}
% Weird issue with endfloat means these need to have no white space

@@

    \begin{figure}[!htbp]
      \centering
      \includegraphics[width=10cm, height=10cm, keepaspectratio=true]{Figures/OhYou_Figure2.pdf}
      \caption{The number of taxa in phylogenies used to fit OU models in ecology, evolutionary biology and palaeontology papers published between 2005 and 2014. Two studies with \textgreater 3000 taxa have been omitted for clarity. See Supporting Information for details.
      }
      \label{figure:ntaxa}
\end{figure} 
% Weird issue with endfloat means these need to have no white space

@@

\noindent
\textbf{Figure 1}: The number of ecology, evolutionary biology and palaeontology papers published between 2005 and 2014 containing the phrase ``Ornstein-Uhlenbeck'', as a proportion of the total number of ecology, evolutionary biology or palaeontology papers published that year. See Supporting Information for details.

>>>>

\usepackage[osf]{mathpazo} % palatino
\usepackage{ms}            % load the template
\usepackage[round]{natbib} % author-year citations
\usepackage{graphicx}
\usepackage{parskip} 
\usepackage{enumerate} 
\usepackage{longtable}
\usepackage{pdflscape}
\usepackage{fullpage}
\usepackage{hyperref}
\usepackage[nomarkers, nolists]{endfloat}  % To push floats to the end   
\pagenumbering{arabic}

@@

    %\begin{figure}[!htbp]
     % \centering
      %\includegraphics[width=10cm, height=10cm, keepaspectratio=true]{Figures/OhYou_Figure1.pdf}
      %\caption{The number of ecology, evolutionary biology and palaeontology papers published between 2005 and 2014 containing the phrase ``Ornstein-Uhlenbeck'', as a proportion of the total number of ecology, evolutionary biology or palaeontology papers published that year. See Supporting Information for details.
      %}
      %\label{figure.literature}
%\end{figure}
% Weird issue with endfloat means these need to have no white space

@@

 %   \begin{figure}[!htbp]
  %    \centering
   %   \includegraphics[width=10cm, height=10cm, keepaspectratio=true]{Figures/OhYou_Figure2.pdf}
    %  \caption{The number of taxa in phylogenies used to fit OU models in ecology, evolutionary biology and palaeontology papers published between 2005 and 2014. Two studies with \textgreater 3000 taxa have been omitted for clarity. See Supporting Information for details.
     % }
      %\label{figure:ntaxa}
%\end{figure} 
% Weird issue with endfloat means these need to have no white space

@@

\noindent
\textbf{Figure 1}: The number of ecology, evolutionary biology and palaeontology papers published between 2005 and 2014 containing the phrase ``Ornstein-Uhlenbeck'', as a proportion of the total number of ecology, evolutionary biology or palaeontology papers published that year. See Supporting Information for details.\\
